---
title: "Descriptive Narratives"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Descriptive Narratives}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(narrator)
library(dplyr)
library(knitr)
```

# Descriptive Narrative

Basic narrative type is descriptive stats, looking into outliers or biggest contributors to the total volumes in the data set. This narratives are quite useful and can help to look deeper into the data set hierarchy.

## Simple Table

Starting with a simplest table that has only one dimension and one measure. Here overall sales volume as well as outlying Territories will be analyzed.
```{r}
df_one <- sales %>%
  group_by(Region) %>%
  summarise(Sales = sum(Sales, na.rm = TRUE)) %>%
  arrange(desc(Sales))

kable(df_one)
```

```{r}
narrate_descriptive(df_one)
```

## Summarization

There are multiple summarization/aggregation options for the data frame, controlled by `summarization` argument that can be `sum`, `count` or `average`

```{r}
sales %>%
  narrate_descriptive(
    measure = "Sales", 
    dimensions = "Region",
    summarization = "count"
  )
```

```{r}
sales %>%
  narrate_descriptive(
    measure = "Sales", 
    dimensions = "Region", 
    summarization = "average"
  )
```

## Multiple Dimensions

```{r}
df_two <- sales %>%
  filter(Region %in% c("NA", "EMEA")) %>%
  group_by(Region, Product) %>%
  summarise(Sales = sum(Sales, na.rm = TRUE)) %>%
  arrange(desc(Sales))

kable(df_two)
```

```{r}
narrate_descriptive(df_two)
```

## Depth

Narration depth can be controlled with `narration_depth` argument. To get summary narratives only set `narration_depth = 1`
```{r}
narrate_descriptive(
  df_two, 
  narration_depth = 1
)
```

## Coverage

Key argument for all narratives is `coverage`. It is used to narrate the most important things and avoid simple looping through all of the dimension levels. <br> <br>
By default coverage is set to 0.5 and this means that narration will stop as soon as cumulative sum reaches 50 % mark. With increased coverage, additional narrative is returned.

```{r}
df_three <- sales %>%
  group_by(Product) %>%
  summarise(Sales = sum(Sales, na.rm = TRUE)) %>%
  arrange(desc(Sales))

df_three %>%
  mutate(
    Share = round(Sales/sum(Sales)*100, 1),
    Cumulative = cumsum(Share)) %>%
  kable()
```

```{r}
narrate_descriptive(df_three)
```

```{r}
narrate_descriptive(df_three, coverage = 0.7)
```
