---
title: "Narrate Echarts Plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Narrate Echarts Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(narrator)
library(dplyr)
library(purrr)
library(echarts4r)
```

Adding narratives helps to extract insights from the data, improve your web applications in Shiny or other framework or reporting in Rmarkdown or Quarto. You can also build more compelling stories together with your plots by adding the text narrative to it. 

Here we will use [echarts4r](https://echarts4r.john-coene.com) by John Coene, one of the best visualization packages build on top of Apache Echarts.


## Simple Plots

Let's create a bar plot out of the `sales` data:
```{r}
barplot <- sales %>%
  dplyr::group_by(Region) %>%
  dplyr::summarise(Sales = sum(Sales)) %>%
  echarts4r::e_chart(Region) %>%
  echarts4r::e_bar(Sales) %>%
  echarts4r::e_tooltip()

barplot
```


We can extract the underlying data from a plot object using `echarts4r::e_get_data()` function and convert it to tibble which will be suitable for our narrative extraction.

```{r}
bar_narrative <- barplot %>%
  echarts4r::e_get_data() %>%
  purrr::map_df(bind_rows) %>%
  narrate_descriptive()

bar_narrative
```

Then we can add this narrative to the plot with `echarts4r::e_text_g()`
```{r}
bar_narrative <- bar_narrative %>%
  unlist(use.names = FALSE) %>%
  paste("\n", collapse = "") 

barplot %>%
  echarts4r::e_text_g(
    style = list(
      text = bar_narrative,
      fontSize = 16
    ),
    left = "2%",
    top = "3%",
    rotation = 0
  )
```

Same can be done for scatter plot and pie chart, for scatter `narrate_descriptive()` will take on the the first numeric measure.

```{r}
scatterplot <- sales %>%
  dplyr::group_by(Region, Product) %>%
  dplyr::summarise(Sales = sum(Sales),
            Quantity = sum(Quantity),
            Price = mean(Price), .groups = "keep") %>%
  echarts4r::e_chart(Sales) %>%
  echarts4r::e_scatter(Quantity, Price) %>%
  echarts4r::e_tooltip()

scatterplot
```

```{r}
scatterplot %>%
  echarts4r::e_get_data() %>%
  purrr::map_df(bind_rows) %>%
  narrate_descriptive()
```


```{r}
piechart <- sales %>%
  dplyr::group_by(Product) %>%
  dplyr::summarise(Sales = sum(Sales)) %>%
  echarts4r::e_chart(Product) %>%
  echarts4r::e_pie(Sales, radius = c("50%", "70%")) %>%
  echarts4r::e_tooltip()

piechart
```

```{r}
piechart %>%
  echarts4r::e_get_data() %>%
  purrr::map_df(bind_rows) %>%
  narrate_descriptive()
```
