---
title: "Formatting Output"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Formatting Output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(narrator)
library(dplyr)
library(htmltools)
```

You can use the output of `narrator` in HTML reports or shiny with additional formatting that can be added using `format_pct()` and `add_tag()` functions. If the output is a named list, which is a default behaviour of the `narrate_*` functions, names can be used as headers and narratives rendered below.

When using `to_html()` function you can easily add formatting for tags and percentage to be displayed is any color you choose:

```{r}
narrative <- sales %>%
  group_by(Region, Product) %>%
  summarise(Sales = sum(Sales, na.rm = TRUE)) %>%
  arrange(desc(Sales)) %>%
  narrate_descriptive()

to_html(narrative)
```

```{r}
to_html(narrative, title_tag = "h5", positive = "purple")
```

Narrator will also convert the output from Chat GPT and replace the new lines with a double `<br>` tag to ensure it is correctly indexed.
```{r}
"The Total Sales across all Products amounted to an impressive $11,381,210.7, with Home and Tools emerging as the top performing categories by Sales with $4,599,370.9 (40.4%) and $4,404,196.7 (38.7%) respectively.\n\nFurther analysis reveals that in the Home category, the North American (NA) and Europe, Middle East and Africa (EMEA)." %>%
  to_html()
```
