---
title: "Editing Templates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Editing Templates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(narrator)
library(dplyr)
library(knitr)
```

## Changing Templates

Template-based systems are based on calculations of individual variables, and combining them together inside of the template. You can return a list of calculated variables and full narrative realization: 
```{r}
df <- sales %>%
  group_by(Product) %>%
  summarise(Sales = sum(Sales, na.rm = TRUE)) %>%
  arrange(desc(Sales))

narrate_descriptive(df, coverage = 0.7, return_data = TRUE)
```

Let's change a template for our narrative function and rework the wording as well as changing 'is' to 'are' since `Sales` is plural:
```{r}
narrate_descriptive(
  df,
  template_total = "Overall {measure} for all {pluralize(dimension_one)} are equal to {total}. ")
```

```{r}
sales %>%
  narrate_descriptive(
    template_outlier = "Among {pluralize(dimension)} {outlier_levels} is an outlier, with {measure} of {outlier_values}, making it {outlier_values_p} of total.",
    template_outlier_multiple = "{outlier_levels} are the biggest {dimension} by {measure} with {outlier_values} or {outlier_values_p} share of total {measure} respectively.",
    measure = "Sales",
    dimensions = c("Region", "Product"),
    coverage = 0.4)
```

### R Environment

We can set the templates using `usethis::edit_r_environ()` or setting up an environment variable using your data science platform capabilities.

```{r eval=FALSE}
Sys.getenv("descriptive_template_total")

narrate_descriptive(
  df,
  template_total = Sys.getenv("descriptive_template_total")
)
```

A method that is a little more handy is setting `.Renviron` variable names using a certain convention and adding `use_renviron = TRUE` to the narrate function. For example here we created a variable that uses the unique part of the function name, underscore, and template name - `descriptive` + `-` + `template_total`
```{r}
narrate_descriptive(
  df, 
  use_renviron = TRUE
)
```

### List Templates

You can get all templates currently available in the package with `list_templates()` function:
```{r}
list_templates() %>%
  kable()
```

### Editing Gadget

Exploring templates might not be an easy task, `narrator` allows to prepare templates interactively using `edit_templates()` function.

```{r eval=FALSE}
edit_templates()
```

### Average vs Others

When `summarization` is set to `average` the way of output calculation is significantly different. Generally better way of using it in your outputs is using different templates for different summarization types.

Giving users control over template creation and avoiding strict ruling for how they should look does introduce some additional complexity. 

For example, if we use a `template_outlier` for default `summarization = "sum"` we get a great descriptive narrative:
```{r}
sales %>%
  narrate_descriptive(
    template_outlier = "Among {pluralize(dimension)} {outlier_levels} is an outlier, with {measure} of {outlier_values}, making it {outlier_values_p} of total.",
    measure = "Sales",
    dimensions = "Region",
    coverage = 0.3)
```

But when trying the same for `summarization = "average"` we get into trouble, because for this case we compare the values for every level to the overall average Sales. Default templates handle that using logic in the `{outlier_insight}` calculation.

```{r}
sales %>%
  narrate_descriptive(
    template_outlier = "Among {pluralize(dimension)} {outlier_levels} is an outlier, with {measure} of {outlier_values}, making it {outlier_values_p} of total.",
    measure = "Sales",
    dimensions = "Region",
    summarization = "average",
    coverage = 0.3)
```


So here we can using something like this:

```{r}
sales %>%
  narrate_descriptive(
    template_outlier = "Among {pluralize(dimension)} {outlier_levels} is an outlier, with average {measure} of {outlier_values}, {outlier_values_p} lower than average {measure} across all records.",
    measure = "Sales",
    dimensions = "Region",
    summarization = "average",
    coverage = 0.3)
```
