---
title: "Trend Narratives"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trend Narratives}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(narrator)
library(dplyr)
library(knitr)
```

# Trend Narrative

When looking into data set with a date or datetime fields, narrator is exploring changes that happen to selected measure in time. Here is a glimpse of such a data set:

```{r}
df <- sales %>%
  dplyr::mutate(Date = lubridate::floor_date(Date, unit = "month")) %>%
  dplyr::group_by(Region, Product, Date) %>%
  dplyr::summarise(Sales = sum(Sales, na.rm = TRUE))

df %>%
  head() %>%
  kable()

```

Default narrative returned will be analyzing year-to-date (YTD) vs prior year-to-date (PYTD) volumes, based on the data set date range. So current year will be considered to be the max date of supplied data.
```{r}
narrate_trend(df)
```

Different time frame can be selected using `type` argument of `narrate_trend()` function. Both numeric and string values are accepted, where 1 stands for 'yoy', 2 for 'previous period', 3 for 'same period last year'. 

When `previous period` is selected, we compare volumes from December 2021 to November 2021:
```{r}
narrate_trend(df, type = "previous period")
```

Alternatively, we can use numeric option, if you are more comfortable with it. Here the function will get December 2020 data for comparison:
```{r}
narrate_trend(df, type = 3)
```
